### 2019-12-11 Statistical Methods/03_graphical-summaries.rmd
statistical methods, ch 3
statistical methods, ch 3
finished graphical summaries
finished graphical summaries

@@

@@

@@

@@

@@

For the boxplot in Figure _3.11_, determine approximately, the quartiles, the interquartile range, and the median.

Approximately how large is the largest value not declared an outlier?

@@

In Figure _3.11_, about how large must a value be to be declared an outlier? How small?

@@

@@

@@

@@

@@

@@

>>>>

_Histograms are not always useful in detecting outliers_

@@

```{r, echo = T}
scores <- c(83, 69, 82, 72, 63, 88, 92, 81, 54,
            57, 79, 84, 99, 74, 86, 71, 94, 71,
            80, 51, 68, 81, 84, 92, 63, 99, 91)
```

@@

```{r, echo = T}
stem(scores)
```

@@

_34.6_

@@

There would only be one stem:

```{r, echo = T}
stem(x, scale = 1/10)
```

@@

For the boxplot in Figure _3.11_, determine approximately, the quartiles, the interquartile range, and the median. _M = 80, Q1/Q2 = 50/121, IQR = 71_

Approximately how large is the largest value not declared an outlier? _215_

@@

In Figure _3.11_, about how large must a value be to be declared an outlier? _x > 227.5_

How small? _x < -56.5_

@@

```{r, echo = T, fig.width=8, fig.height=4}
data <- data.table::fread(paste0(data.dir, "film_dat.txt"), fill = T)

p1 <- ggplot(values, aes(y = value)) +
   geom_boxplot(fill = "cornflowerblue") +
   labs(title = "Film Ratings")

p2 <- ggplot(values, aes(x = value)) +
   geom_bar(aes(y = ..prop..), fill = "cornflowerblue", width = 0.05) +
   labs(title = "Film Ratings")

grid.arrange(p1, p2, nrow = 2)

@@

```{r, echo = T, fig.width=8, fig.height=4}
data <- data.table::fread(paste0(data.dir, "mismatch_dat.txt"), fill = T)

p1 <- ggplot(values, aes(y = value)) +
   geom_boxplot(fill = "cornflowerblue") +
   labs(title = "T5 Mistmatch")

p2 <- ggplot(values, aes(x = value)) +
   geom_histogram(aes(y = ..density.., fill = ..count..), bins = 30) +
   geom_density(fill = "darkorange", alpha = .3) +
   labs(title = "T5 Mistmatch Density")

grid.arrange(p1, p2, nrow = 2)

@@

_The population follows a symmetric distribution and outliers are rare._

@@

_There are numerical estimators avalaible using bootstrapping techniques, however, a general rule of thumb is > 100._

@@

_A boxplot is generally better at showing outliers_.

@@

_Not always. A population could be symetric and a given sample could be skewed._
